Scoring Patients

### 2018-04-16 Patient Report.Rmd
updating Rstudio app

var.seg.lengths = lapply(patient.data, function(df) {
  cbind('chr'=df$variable.regions$chrom, 'start'=df$variable.regions$start.pos, 'end'=df$variable.regions$end.pos, 'seg.len'=df$variable.regions$end.pos - df$variable.regions$start.pos)
})

@@

ggplot(df, aes(status, seg.len)) + geom_jitter(aes(color=status), alpha=0.5, show.legend = F, width=.2) +
  geom_boxplot(aes(group=status, fill=status), show.legend=F, outlier.colour = NA) + 
  geom_label(data=subset(df, status == 'Progressor'), aes(status, max(seg.len)-2*sd(seg.len), label=paste('median\n',scientific(median(seg.len),3),sep='') )) +
  geom_label(data=subset(df, status == 'Non-Progressor'), aes(status, max(seg.len), label=paste('median\n',scientific(median(seg.len),3),sep=''))) +
  labs(y='Variable segment length', x='', title='Variable regions', caption=paste('Wilcox p-value', signif(lenWT$p.value, digits=3) ))

ggplot(df, aes(status, seg.len)) + 
  geom_jitter(aes(color=status), show.legend=F) + geom_violin(aes(group=status, fill=status), show.legend=F) +
  geom_label(data=subset(df, status == 'Progressor'), aes(status, max(seg.len)-2*sd(seg.len),label=paste('median\n',scientific( median(seg.len) , 3),sep='') ))  +
    geom_label(data=subset(df, status == 'Non-Progressor'), aes(status, max(seg.len), label=paste('median\n',scientific( median(seg.len) , 3),sep=''))) +
    labs(y='Variable segment length', x='', title='Variable regions', caption=paste('Wilcox p-value', signif(lenWT$p.value, digits=3) ))

@@

```{r, echo=F, warning=F, message=F}
df = rbind(cbind.data.frame('n'=sapply(var.seg.lengths[prog.pt], nrow), 'status'='Progressor'), cbind.data.frame('n'=sapply(var.seg.lengths[np.pt], nrow), 'status'='Non-Progressor'))
nWT = wilcox.test(subset(df, status == 'Progressor')$n, subset(df, status == 'Non-Progressor')$n)

ggplot(df, aes(status, n, group=status)) + geom_jitter(aes(color=status), width=0.2) +
  geom_boxplot(aes(fill=status), position = 'dodge', show.legend = F, outlier.colour = NA) +
  geom_label(data=subset(df, status == 'Progressor'), 
             aes(status, max(n)-2*sd(n), label=paste('median\n',sprintf("%.1f",median(n)),sep=''), fill=status ), color='white' ) +
  geom_label(data=subset(df, status == 'Non-Progressor'), 
             aes(status, max(n)+2*sd(n), label=paste('median\n',sprintf("%.1f",median(n)),sep=''), fill=status), color='white') +
  labs(y='Number of segments', title="Total number of segments", caption=paste('Wilcox p-value', signif(nWT$p.value, digits=3)) ) +
  theme(legend.position = 'none')

ggplot(df, aes(status, n, group=status)) + geom_jitter(aes(color=status), width=0.2) +
  geom_violin(aes(fill=status, group=status)) +
  geom_label(data=subset(df, status == 'Progressor'), 
             aes(status, max(n)-2*sd(n), label=paste('median\n',sprintf("%.1f",median(n)),sep=''), fill=status ), color='white' ) +
  geom_label(data=subset(df, status == 'Non-Progressor'), 
             aes(status, max(n)+2*sd(n), label=paste('median\n',sprintf("%.1f",median(n)),sep=''), fill=status), color='white') +
  labs(y='Number of segments', title="Total number of segments", caption=paste('Wilcox p-value', signif(nWT$p.value, digits=3)) ) +
  theme(legend.position = 'none')

>>>>

var.seg.lengths = lapply(patient.data, function(pt) {
  cbind('chr'=pt$variable.regions$chrom, 'start'=pt$variable.regions$start.pos, 'end'=pt$variable.regions$end.pos, 'seg.len'=pt$variable.regions$end.pos - pt$variable.regions$start.pos)
})

@@

m = (melt(df, id.vars = 'status', measure.vars = 'seg.len'))
m2 = m %>% group_by(status) %>% summarise( median=median(value), n=length(status), value=max(value) )
ggplot(m, aes(status, value, group=status, fill=status)) + geom_jitter(aes(color=status), width=.2) + geom_violin(alpha=0.5) +
  geom_label(data=m2, aes(status, value, label=paste("median=",scientific(median,3),'\nn=',n, sep='')), fill='white') + 
  theme(legend.position = 'none') + labs(y='Variable segment length', x='', title=paste('Length of variable regions (all samples n=',length(patient.info$Samplename),')',sep=''), subtitle=paste('Wilcox p-value', signif(lenWT$p.value, digits=3) ))

@@

```{r, echo=F, warning=F, message=F}
df = rbind(cbind.data.frame('n'=sapply(var.seg.lengths[prog.pt], nrow), 'status'='Progressor'), cbind.data.frame('n'=sapply(var.seg.lengths[np.pt], nrow), 'status'='Non-Progressor'))
nWT = t.test(subset(df, status == 'Progressor')$n, subset(df, status == 'Non-Progressor')$n)

ggplot(df, aes(status, n, group=status)) + geom_jitter(aes(color=status), width=0.2) +
  geom_violin(aes(fill=status, group=status), alpha=0.5) +
  geom_label(data=(df %>% group_by(status) %>% summarise(y=max(n), med=median(n))), 
             aes(status, y, label=paste('median\n',sprintf("%.1f", med, sep='')))) +
  labs(y='Number of segments', title="Number of segments per patient", subtitle=paste('t-test p-value', signif(nWT$p.value, digits=3)) ) +
  theme(legend.position = 'none')

nohgd.var.seg.lengths = lapply(patient.data, function(pt) {
  samples = subset(pt$info, Pathology %in% c('BE','ID','LGD'))$Samplename
  cols = c('chrom','start.pos','end.pos', grep(paste(samples, collapse='|'), colnames(pt$variable.regions), value=T))
  vr = pt$variable.regions[,cols]

  cbind('chr'=vr$chrom, 'start'=vr$start.pos, 'end'=vr$end.pos, 'seg.len'=vr$end.pos - vr$start.pos)
})
